% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\usepackage{hyperref}
\robustify\cftdotfill

%-----------------------------------------------------------
%Edit these values as you see fit
\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------
%Margin setup
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{-0.25in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.75in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadingTwo}[2]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2
\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------
\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

\textbf{\Large Rifat Shahriyar}\\
\texttt{Associate Professor}\\
\texttt{Department of Computer Science and Engineering}\\
\texttt{Bangladesh University of Engineering and Technology}\\
\texttt{rifat@cse.buet.ac.bd, rifat.shahriyar@gmail.com}\\ \texttt{\href{http://rifatshahriyar.github.io}{rifatshahriyar.github.io}} \\

\end{tabular*}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Research Interests}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
My research interests are memory management specially garbage collection, programming language, virtual machine, and high performance computing.


\resheading{Employment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item
	\ressubheading{Bangladesh University of Engineering and Technology}
	{Dhaka, Bangladesh}
	{Associate Professor, Department of Computer Science and Engineering}
	{Oct 2017 - Date}

\item
	\ressubheading{Bangladesh University of Engineering and Technology}
	{Dhaka, Bangladesh}
	{Assistant Professor, Department of Computer Science and Engineering}
	{May 2010 - Oct 2017}

\item
	\ressubheading{Bangladesh University of Engineering and Technology}
	{Dhaka, Bangladesh}
	{Lecturer, Department of Computer Science and Engineering}
	{June 2007 - May 2010}
	
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{Australian National University}{Canberra,
          Australia}{Ph.D. in Computer Science}{September 2010 - April 2015}
	\begin{itemize}
	\resitem{Thesis: High Performance Reference Counting and Conservative Garbage Collection}
		\resitem{Supervisors: Prof. Steve Blackburn and Prof. Kathryn McKinley}
	\end{itemize}

\item
	\ressubheading{Bangladesh University of Engineering and Technology}{Dhaka, Bangladesh}
	{M.Sc. in Computer Science and Engineering}{October 2007 - December 2009}
	\begin{itemize}
		\resitem{Thesis: A Distributed Optimized Resource Reservation Scheme for Grid Computing}
		       \resitem{Supervisor: Prof. Md. Mostofa Akbar}
	\end{itemize}

\item
	\ressubheading{Bangladesh University of Engineering and Technology}{Dhaka, Bangladesh}
	{B.Sc. in Computer Science and Engineering}{April 2002 - May 2007}
	\begin{itemize}
		\resitem{Thesis: Controlling Remote Systems using Mobile Telephony}
                \resitem{Supervisor: Prof. Md. Mostofa Akbar}
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Publications}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item S. A. Hassan, D. Das, A. Iqbal, A. Bosu, {\bf R. Shahriyar}, and T. Ahmed, {\color{black} \bf
    ``SOQDE: A Supervised Learning based Question Difficulty Estimation Model for Stack Overflow"}, in Proceedings of the 25th Asia-Pacific Software Engineering Conference, APSEC 2018, Nara, Japan, 2018. 
    
\item P. Chakraborty, {\bf R. Shahriyar}, A. Iqbal, and A. Bosu, {\color{black} \bf
    ``Understanding the Software Development Practices of Blockchain Projects: A Survey"}, in Proceedings of the 12th International Symposium on Empirical Software Engineering and Measurement, ESEM 2018, Oulu, Finland, 2018.

\item Z. Mehrab, R. B. Yousuf, I. A. Tahmid, and {\bf R. Shahriyar}, {\color{black} \bf
    ``Mining Developer Questions about Major Web Frameworks"}, in Proceedings of the 14th International Conference on Web Information Systems and Technologies, WEBIST 2018, Seville, Spain, 2018.

\item N. S. Sattar, T. Aqila, and {\bf R. Shahriyar}, {\color{black} \bf
    ``Towards concurrent data structure development with Relaxed Synchronization"}, in Proceedings of the 9th International Conference on Electrical and Computer Engineering, ICECE 2016, Dhaka, Bangladesh, 2016.

\item B. Islam, F. Hossain, and {\bf R. Shahriyar}, {\color{black} \bf
    ``High Performance Approximate Computing by Adaptive Relaxed Synchronization"}, in Proceedings of 18th IEEE International Conference on High Performance Computing and Communications, HPCC 2016, Sydney, Australia, 2016.
        
\item M. Tasnim, {\bf R. Shahriyar}, N. Nahar, and H. Mahmud,  {\color{black} \bf
    ``Intelligent Depression Detection and Support System: Statistical Analysis, Psychological Review and Design Implication"}, in Proceedings of IEEE 18th International Conference on e-Health Networking, Applications and Services, Healthcom 2016, Munich, Germany, September 14-16, 2016.     

\item A. Sultana, M. Naznin, and {\bf R. Shahriyar}, {\color{black} \bf
    ``Conflicting Goal Constrained Architecture of a Heterogeneous Mobile Sensor Network"}, in Proceedings of the 2nd International Conference on Networking Systems and Security, NSysS 2016, Dhaka, Bangladesh, 2016.

\item M. R. Haque, M. Naznin, and {\bf R. Shahriyar}, {\color{black} \bf
    ``Distributed Low Overhead ID in a Wireless Sensor Network"}, in Proceedings of the 17th International Conference on Distributed Computing and Networking, ICDCN 2016, Singapore, 2016.

\item {\bf R. Shahriyar}, S. M. Blackburn, and K. S. McKinley,  {\color{black} \bf
    ``Fast Conservative Garbage collection'}, ACM SIGPLAN Notices, 
vol. 49, iss. 10, p. 121-139, 2014.

\item {\bf R. Shahriyar}, S. M. Blackburn, and K. S. McKinley,  {\color{black} \bf
    ``Fast Conservative Garbage collection'}, in Proceedings of the 25th ACM SIGPLAN conference on Object Oriented Programming Systems, Languages and Applications, OOPSLA '14, Portland, USA, 2014.

\item {\bf R. Shahriyar}, S. M. Blackburn, X. Yang, and K. S. McKinley, {\color{black} \bf
    ``Taking Off the Gloves with Reference Counting Immix"},  ACM SIGPLAN Notices, 
vol. 48, iss. 10, p. 93-110, 2013.

\item {\bf R. Shahriyar}, S. M. Blackburn, X. Yang, and K. S. McKinley, {\color{black} \bf
    ``Taking Off the Gloves with Reference Counting Immix"},  in Proceedings of the 24th ACM SIGPLAN conference on Object Oriented Programming Systems, Languages and Applications, OOPSLA '13, Indianapolis, USA, 2013.

\item {\bf R. Shahriyar}, S. M. Blackburn, and D. Frampton,  {\color{black} \bf
    ``Down for the Count? Getting Reference Counting Back in the Ring"}, in Proceedings of the Eleventh ACM SIGPLAN International Symposium on Memory Management, ISMM '12, Beijing, China, June 15-16, 2012.

\item {\bf R. Shahriyar}, M. M. Akbar, M. S. Rahman, M. F. Bari, and S. Shahriyar, {\color{black} \bf
    ``CORS - A Cost Optimized Resource Reservation Scheme for Grid"}, in Proceedings of the International Conference on Parallel and Distributed Processing Techniques and Applications, PDPTA '11, Las Vegas, Nevada, USA, July 18-21, 2011. 

\item {\bf R. Shahriyar}, M. F. Bari, G. Kundu, S. I. Ahamed, and M. M. Akbar,  {\color{black} \bf
    ``Intelligent Mobile Health Monitoring System (IMHMS)"}, International Journal of Control and Automation (IJCA), vol. 2, iss. 3, 2009. 
    
\item {\bf R. Shahriyar}, M. F. Bari, G. Kundu, S. I. Ahamed, and M. M. Akbar,  {\color{black} \bf
    ``Intelligent Mobile Health Monitoring System (IMHMS)"}, in Proceedings of Second International ICST Conference on Electronic Healthcare for the 21st century, eHealth 2009, Istanbul, Turkey, September 23-15, 2009.


\item S. Sultana, R. Karim, {\bf R. Shahriyar}, M. M. Akbar, and S. I. Ahamed,  {\color{black} \bf
    ``Ubiquitous Secretary: A Ubiquitous Computing Application based on Web Services Architecture"}, International Journal of Multimedia and Ubiquitous Engineering (IJMUE), vol. 4, iss. 4, 2009. 
    
\item M. F. Bari, M. S. Rahman, and {\bf R. Shahriyar},  {\color{black} \bf
    ``Finding all covers of an indeterminate string in O(n) time on average"}, in Proceedings of the Prague Stringology Conference, PSC 2009, Prague, Czech Republic, August 31 - September 2, 2009. 

\item {\bf R. Shahriyar}, E. Hoque, I. Naim, S. Sohan, M. M. Akbar, and M. Khan,  {\color{black} \bf
    ``Controlling Remote Systems using Mobile Telephony"}, International Journal of Smart Home (IJSH), vol. 2, iss. 3, 2008. 
    
\item {\bf R. Shahriyar}, E. Hoque, I. Naim, S. Sohan and M. M. Akbar, {\color{black} \bf
    ``Controlling Remote Systems using Mobile Telephony"}, in Proceedings of the 1st International Conference on MOBILe Wireless MiddleWARE, Operating Systems, and Applications, Mobilware 2008, Innsbruck, Austria, February 13 - 15, 2008. 


\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Awards and Honours}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item ACM SIGPLAN PAC Grant to attend ASPLOS 2015

\item ACM SIGPLAN PAC Grant to attend OOPSLA 2013

\item ANU Vice-Chancellor's HDR Travel Grant to attend ISMM and PLDI 2012

\item ANU University Research Scholarship (2010 - 2014)

\item ANU Research Supplementary Scholarship (2010 - 2014)

\item Endeavour International Postgraduate Research Scholarship from University of Melbourne (2010 - 2014, Not Availed)

\item University of Melbourne International Research Scholarship (2010 - 2014, Not Availed)

\item University Merit Scholarships in Bangladesh University of Engineering and Technology for academic results

\item Dean's Award in Bangladesh University of Engineering and Technology for academic results

\item Board Scholarships from Board of Secondary and Higher Secondary Education, Dhaka, Bangladesh

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Research Experiences}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{itemize}

\item
	\ressubheading{Australian National University}{Canberra,
          Australia}{Ph.D. in Computer Science}{September 2010 - April 2015}
	\begin{itemize}
	
	       \resitem {Designed and implemented several optimizations for reference counting.  Reference counting is almost completely ignored in implementations of high performance systems today. We find that an existing modern implementation of reference counting has average 30\% overhead compared to tracing. Our optimizations completely eliminate that overhead and brings the performance of reference counting on par with that of a well-tuned mark-sweep collector. ({\bf ISMM 2012})}


		\resitem {Designed and implemented our improved reference counting in Immix heap organization. Reference counting generally use free list for allocation. Immix is a mark-region based garbage collector that uses bump pointer for allocation, tracing for identification and sweep-to-region for reclamation. The proposed RC Immix collector will use bump pointer for allocation, reference counting for identification, sweep-to-region for reclamation, and performs defragmentation both proactively and reactively. It outperforms the production garbage collector of Jikes RVM. ({\bf OOPSLA 2013})}
		
                \resitem {Designed and implemented a conservative garbage collector for managed languages based on RC Immix. The existing conservative garbage collectors like Boehm-Demers-Weiser (BDW) and Mostly Copying (MCC) suffer significant performance overhead compared to exact generational tracing collectors. Our conservative RC Immix collector uses a low overhead object map to validate ambiguous references and pin their referents with Immix line granularity. It matches the performance of the production garbage collector of Jikes RVM. ({\bf OOPSLA 2014})}


	\end{itemize}

\item
	\ressubheading{Oracle Labs}{California, USA}{Research Intern}{May 2013 - August 2013}
	\begin{itemize}
          \resitem {Designed and implemented a garbage collector for Oracle's Substrate VM.}

          
	\end{itemize}


\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\resheading{Teaching Experiences}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item Structured Programming Language (Reference Language: C)

\item Object Oriented Programming Language (Reference Language: C++ and Java)
 
\item Data Structures

\item Database

\item Computer Architecture

\item Programming Languages and Systems (Graduate Course)

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Community Services}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
  \item
  \ressubheadingTwo{Program Committee Member}{}
  \begin{itemize}
  \resitem{ISMM 2015}
  \end{itemize}
\end{itemize}

\end{document}
